cardinalR: Generating interesting high-dimensional data structures

### 2025-10-08 paper-cardinalR.Rmd
Updated the branching projection

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.8, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.085,
                                              axis_scaled = 6, 
                                              axis_pos_x = -0.07, 
                                              axis_pos_y = -0.07, 
                                              threshold = 0.006))

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.1, 0.1), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

>>>>

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.8, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.15,
                                              axis_scaled = 10, 
                                              axis_pos_x = -0.12, 
                                              axis_pos_y = -0.12, 
                                              threshold = 0.015))

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.15, 0.15), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)
